Condensed Matter Field Theory notes

### 2017-03-01 Condensed Matter Field Theory note/CMF-Atland.tex
[minor] today's notes about Atland's CMP Field theory

\maketitle
\abstract{
Notes of book \cite{Altland2010a}.
}
\tableofcontents

\section{pp.33 eq.1.43}
\label{sec:Table}

In page 33 of \cite{Altland2010a}, the author derives a difference of action, when we
have a symmetry transformation paraterized by $\omega_a$:

@@

Therefore, the term we seek, i.e. the coefficient of $\partial_\mu\omega_a$ is
\begin{align}
  & \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
    \left(
        F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
        \partial_\nu(\phi^i+F^i_a\omega_a)
    \right)
    +
    \frac{\partial x_\mu}{\partial \omega_a}\mathcal{L} \\
    =&
    \left(
        \mathcal{L}\delta_{\mu\nu}
        -\frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
            \partial_\nu \phi^i
    \right) \frac{\partial x_\nu}{\partial \omega_a}
    +
    \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}F^i_a
\end{align}
which is what we expect in equation 1.43 of \cite{Altland2010a}.

@@

It is not so obvious to get Eq.3.5 in pp.99 of \cite{Altland2010a}. Here is my
notes.

@@

The Hamiltonian for particle on a ring is claimed to be (Eq. 9.1 of
\cite{Altland2010a}, pp. 498):
\begin{equation}
    H = \frac{1}{2}(-i\partial_\phi -A)^2 = \frac{1}{2}(p-A)^2
\end{equation}

The book \cite{Altland2010a} claims that 
\begin{equation}
    L = \frac{1}{2}\dot{\phi}^2 - iA \dot{\phi}
\end{equation}
I am quite confused, especially about the appearance of $\dot{\phi}$. Can any explain
a bit?

@@

\bibliography{cite}{}
\bibliographystyle{alpha}

>>>>

\maketitle
\abstract{
Notes of book \cite{Altland2010}, and another book \cite{Greiner1996} for
information about path integral.
}
\tableofcontents

\section{Todo}

\begin{enumerate}
    \item Understand in what case can the Gaussian integral formula can be
        applied. In another word, understand the analytical continuation of the
        Gaussian integral. See for example, buttom of pp.343 of
        \cite{Greiner1996}.
        \label{todo:analytical-c}
    \item Understand the Wick Rotation, cf. pp.356(ch11.5) of
        \cite{Greiner1996}. This is related to todo \ref{todo:analytical-c}
    \item Understand how the constant term in the path integral of a Feynman
        Kernal will(or will not) affect the physics. Understand the mathematical
        rationale to support this. (cf. buttom of pp.344 of \cite{Greiner1996}.
    \item I have doubt about the correctness of pp.110 eq 3.28 till pp.111
        (Construction recipe of the path integral), especially about his
        argument, the size of the \textit{Planck cell}.
\end{enumerate}

Bonus objectives:
\begin{enumerate}
    \item Find abou the similarity between Path Integral of a free particle and
        the solution to a classical diffusion equation (cf. pp.112, footnote 1
        of \cite{Altland2010}).
    \item Those marked \textit{todo} in \cite{Altland2010}.
\end{enumerate}
\section{pp.33 eq.1.43}
\label{sec:Table}

In page 33 of \cite{Altland2010}, the author derives a difference of action, when we
have a symmetry transformation paraterized by $\omega_a$:

@@

Therefore, the term we seek, i.e. the coefficient of $\partial_\mu\omega_a$ is
\begin{align}
  & \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
    \left(
        F^i_a-\frac{\partial x_\nu}{\partial \omega_a}
        \partial_\nu(\phi^i+F^i_a\omega_a)
    \right)
    +
    \frac{\partial x_\mu}{\partial \omega_a}\mathcal{L} \\
    =&
    \left(
        \mathcal{L}\delta_{\mu\nu}
        -\frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}
            \partial_\nu \phi^i
    \right) \frac{\partial x_\nu}{\partial \omega_a}
    +
    \frac{\partial \mathcal{L}}{\partial(\partial_{x_\mu}\phi^i)}F^i_a
\end{align}
which is what we expect in equation 1.43 of \cite{Altland2010}.

@@

It is not so obvious to get Eq.3.5 in pp.99 of \cite{Altland2010}. Here is my
notes.

@@

The Hamiltonian for particle on a ring is claimed to be (Eq. 9.1 of
\cite{Altland2010}, pp. 498):
\begin{equation}
    H = \frac{1}{2}(-i\partial_\phi -A)^2 = \frac{1}{2}(p-A)^2
\end{equation}

The book \cite{Altland2010} claims that 
\begin{equation}
    L = \frac{1}{2}\dot{\phi}^2 - iA \dot{\phi}
\end{equation}
I am quite confused, especially about the appearance of $\dot{\phi}$. Can any explain
a bit?

@@

\bibliography{cite}{}
\bibliographystyle{alphaurl}
